Score-based tests of measurement invariance: Use in practice

### 2014-02-03 frontiers/frontiers.Rnw
Frontiers paper: revisions to paper, response letter, and refs
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@312 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Many of the papers in this special issue focus on the topic of approximate
measurement invariance: we know that strict hypotheses of measurement invariance
do not hold exactly across different groups, and this should be reflected in
corresponding tests of measurement invariance.  Under a Bayesian
approach, we may utilize the idea of approximate invariance
\cite<e.g.,>{muthen13}, whereby across-group equality constraints on
parameters are replaced with informative prior distributions.  In this paper, we
describe an alternative approach: the development of test statistics that 
are especially sensitive to violations that are monotonic w.r.t. the
variable of interest (and 
less sensitive to violations that are non monotonic w.r.t. the
variable of interest).  Because monotonic violations are more likely to be
interpretable and interesting to the researcher, we can gain more
power to detect these violations by de-emphasizing other types of violations.
The resulting test statistics are specifically applicable to
situations where one  
wishes to test for measurement invariance with respect to an ordinal variable, 
and they are special cases of a family of tests that may be used to study 
measurement invariance w.r.t.\ continuous, categorical, and ordinal
variables.  Other methods for studying measurement
invariance w.r.t.\ continuous variables include moderated factor
models \cite{bauhus09,moldol10,pur02} and factor mixture models
\cite{dolmaa98,lubmut05}.  These methods require a model of greater
complexity to be estimated, while the tests described here work solely
on the output of a traditional factor model.  See \citeA{MerZei13} for
further comparison of these methods.

The family of tests described in this paper have recently been applied
to the study of measurement invariance \cite{MerZei13,MerFanZei}, though their
practical application has been limited to a small set of simulations and
datasets.  In this paper, we provide a detailed illustration of the tests' use
and performance under
scenarios likely to be encountered in practice.  While the previous
papers have described and studied the tests under ideal conditions, we
focus here on two topics of interest to the applied researcher:
software considerations for carrying out the tests, and test
performance under model misspecification.
%In order to fix the psychometric scale, we need to specify the violating parameter.  
%Moreover, in practice model misspecification is an inevitable issue to a certain extent 
%and may interfere with parameter invariance specificity. A family of tests derived from 
%stochastic process has been recently proposed to identify specific parameters impacted 
%by measurement invariance violation. However, these tests have only been used to a limited 
%type of parameter violation. It is this paper's intent to provide a detailed examination 
%of the tests' performance under practical research scenarios. 
In the following sections, we first briefly review the  theoretical framework of
the proposed tests and provide a short tutorial illustrating the use of the
tests in \proglang{R} \cite{R11}. Next, we study the tests' performance in simulations that mimic
practical research scenarios.  Finally, we provide some further discussion on
the tests' use in practice.

@@

To verbally describe the above equation, each
individual has $k$ scores describing the extent to which the fitted
model describes that particular individual.  We can roughly interpret
scores near zero as providing a ``good'' description of an individual,
with scores far from zero providing a ``bad'' description of an
individual.  This is only a rough interpretation as, even when measurement
invariance holds, some individuals' scores will be further from zero
than others.  However, under measurement noninvariance, the scores
will differ for different subgroups of individuals (say, scores in
subgroup A tend to be negative and scores in subgroup B tend to be
positive).  Each of the $k$ scores represents one model parameter,
which, as further described below, allows us to test subsets of model
parameters for invariance.

To use the scores for testing, we order individuals according to
an auxiliary variable $V$ (the variable against which we are testing 
measurement invariance) and look for ``trends'' in the
scores.  For example, imagine that we are testing
for measurement 
invariance w.r.t.\ age.  If there exists measurement invariance
w.r.t. age, then some parameter estimates may be too large for 
young individuals and too small for old individuals (say).  This
result would be reflected in the scores, where young individuals'
scores may be greater than zero and old individuals' scores 
less than zero (though the sign of the scores will depend on whether a
function is being minimized or maximized).  Conversely, if measurement
invariance holds, then all 
individuals' scores will fluctuate randomly around zero.

@@

In addition to test statistics, ``instability plots'' can be generated
by setting 
\code{plot = TRUE} in the \code{sctest()} calls above. The resulting plots representing
the ordinal statistics' fluctuations across levels of age group are displayed in
Figure~\ref{fig:ordres}.
These plots display the loadings' fluctuation across age groups, with the x-axis
reflecting age group and the y-axis reflecting test statistic values (larger
values reflect more instability).  The dashed horizontal lines reflect critical values, so
that the hypothesis of measurement invariance is rejected if the sequence of
test statistics crosses the critical value.  While the measurement invariance tests are
non-significant, the plots imply some instability in the older age groups (15 and~16).

@@

\section{Simulation 1}
In Simulation 1, we examined the extent to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameter estimates, including factor covariances, intercepts or 
the unique variance associated with the manifest variable in question.  
Thus, the goal of the Simulation 1 is to examine the extent to which 
the proposed tests attribute the measurement invariance violation 
to the parameters that are truly in violation.

@@

To examine these issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of four places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance  ($\psi_{11}$)
 or intercept associated with Scale 1 ($\mu_{11}$)
, the factor covariance ($\phi_{12}$).  Note that the
 latter violation is not necessarily a measurement invariance
 \cite<e.g.,>{mer93}, but it is still a parameter instability that can occur in
 this type of model.
 We then tested for measurement invariance (parameter instability) in
 seven subsets of parameters: each of the four
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
all six unique variances and all six intercepts. % $\epsilon_{11}--\epsilon_{66}$.

@@

Full simulation results are presented in Figures~\ref{fig:sim11res}
to~\ref{fig:sim14res}.
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude in the factor loading $\lambda_{11}$,
with the parameters being tested changing across rows,
the number of levels $m$ of the ordinal variable $V$ across columns,
and lines reflecting different test statistics.
Figure~\ref{fig:sim12res}, Figure~\ref{fig:sim13res} and 
Figure~\ref{fig:sim14res} display 
similar power curves when the factor covariance 
$\phi_{12}$, error variance $\epsilon_{11}$ and intercept
$\mu_{11}$ violate measurement
invariance, respectively. In these figures, we generally show tests
associated with parameters that exhibited nonzero power curves.  For
example, in Figure~\ref{fig:sim11res}, the middle row shows that power
for tests of $\psi_{11}$ stays near zero for all values of $m$ and $d$.
Similar rows have been omitted from this figure and other figures.

@@

From these figures, one generally observes that the tests isolate 
the parameter violating measurement invariance.  Additionally, the tests 
have somewhat higher power to detect measurement invariance violations 
in the factor loading, factor covariance and intercept parameters, 
as opposed to the error variance parameter.  
Finally, simultaneous tests of all factor loadings, all intercepts or 
all error parameters result in decreased power, as compared to the situation
where one tests only the violating parameter.  This occurs because, in
testing a subset of parameters (only one of which violates measurement
invariance), we are effectively dampening the signal of a measurement
invariance violation. This ``dampening'' effect is more apparent for
the $\max \mathit{LM}_o$ statistic, because it involves a sum across
all tested parameters (see Equation~\eqref{eq:maxlmo}).
Conversely, $\mathit{WDM}_o$ takes the maximum over parameters
(Equation~\eqref{eq:wdm}), so that invariant parameters have no
impact on this statistic.

@@

\subsection{Method}
A measurement invariance violation could occur in
each of the four parameters from Simulation 1 (factor loading, factor
covariance, unique variance and intercept), and a violation could also occur in
the extra, unmodeled loading. In each condition, a single parameter
exhibited the violation. 
Sample size and magnitude of measurement invariance violation were manipulated 
in the same way as they were in Simulation 1.  The tested parameters
were also the same as Simulation 1.

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error also demonstrated when testing all loadings and all unique
variances, as shown in the appendix.  Tests
associated with the factor 
covariance and intercept did not demonstrate this error, however.  In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

When the parameter violating measurement invariance was modeled,
results were generally the same as Simulation 1.  
When the modeled factor loading, $\lambda_{11}$, violated measurement
invariance, the statistics were generally able to pick up the violation despite
the misspecification. Similar results were observed
when the unique variance, intercept and factor covariance parameters violated measurement
invariance; these results are all shown in the Appendix.
In particular, the power of ordered statistics $\max \mathit{LM}_o$ test and
$\mathit{WDM}_o$ test showed higher power than unordered $\mathit{LM}_{uo}$ in
each of these panels.

In summary, the proposed test statistics appear robust to unmodeled
loading parameters, so long 
as the unmodeled loading does not violate measurement invariance.  If
the unmodeled loading  
does violate measurement invariance, the tests can still detect
measurement invariance violations.  The violations are assigned to 
modeled parameters that do not violate measurement invariance, however.
The impacted parameters include the error 
variance and other loadings associated with the manifest variable that
has an unmodeled loading.
Thus, as for other tests of measurement invariance, it is important to
study the extent to 
which the hypothesized model includes all parameters of importance.
None of these tests (score-based or otherwise) inform the researcher of
model misspecification.

@@

In the remainder of the paper, we first compare
these tests to traditional tests of measurement invariance.  We then 
discuss test extension to other fit functions and to other specialized
models.

@@

Many of the applications in this volume, along with many measurement
invariance applications in
general, focus on testing across unordered categories
such as nations or gender.  As discussed earlier in this paper, the score-based
tests for unordered categories are essentially equivalent to the usual
likelihood ratio test.  Given a measurement invariance violation across these
unordered categories, however, researchers typically wish to know why the
violation occurred.  At this point, researchers may examine education level,
socioeconomic status, income levels, and so on across the unordered categories. 
These variables are often ordinal or continuous in nature, so that the family of
tests described in this paper are applicable.  This is a first step towards
describing why measurement invariance violations occur, as opposed to simply
detecting measurement invariance violations. 
%% TODO!!
%\readme{In the abstracts for the
%special issue (which the special editors sent us), one paper was proposed along
%these lines.  I will get a draft of that paper and then we can cite it here.}
The tests described here are convenient for this purpose, as they do
not require a new model to 
be estimated for each ordinal variable.  Instead, each ordinal variable defines
an ordering of observations, which in turn yields a test statistic that is
specific to that ordinal variable.

@@

In addition to alternative fit functions, the tests can be extended to other
models estimated via ML.  Of primary interest to the topic of measurement
invariance, the tests can be extended to item response models to examine
differential item functioning.  In particular, \citeA{strkop13} studied
application of these tests to the Rasch model, using them as the basis of a
recursive partioning procedure that segments subgroups of individuals who
exhibit DIF.  Further study and extension of these tests for IRT seem warranted.

@@

This Appendix contains additional results from Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figure~\ref{fig:sim22res} to Figure~\ref{fig:sim26res} display
results when the unmodeled loading, the loading $\lambda_{11}$, the
covariance $\phi_{12}$, the error term $\psi_{11}$ and intercept $\mu_{11}$
violate invariance, respectively.  Results are only shown for simulation
conditions exhibiting power curves that increased from zero.  These
results were generally the same as the Simulation 1 results.

>>>>

Many of the papers in this special issue focus on the topic of approximate
measurement invariance: we know that strict hypotheses of measurement invariance
do not hold exactly across different groups, and this should be reflected in
corresponding tests of measurement invariance.  Under a Bayesian
approach, we may utilize the idea of approximate invariance
\cite<e.g.,>{muthen13}, whereby across-group equality constraints on
parameters are replaced with informative prior distributions.  In this paper, we
describe an alternative approach: the development of test statistics that 
are especially sensitive to violations that are monotonic w.r.t. the
variable of interest (and 
less sensitive to violations that are non-monotonic w.r.t. the
variable of interest).  Because monotonic violations are more likely to be
interpretable and interesting to the researcher, we can gain more
power to detect these violations by de-emphasizing other types of violations.
The resulting test statistics are specifically applicable to
situations where one  
wishes to test for measurement invariance with respect to an ordinal variable, 
and they are special cases of a family of tests that may be used to study 
measurement invariance w.r.t.\ continuous, categorical, and ordinal
variables.

The study of measurement invariance w.r.t.\ categorical auxiliary 
variables (via, e.g., likelihood ratio tests) is popular and well
known, and ordinal auxiliary variables are typically treated as
categorical in measurement invariance contexts.
The study of measurement invariance w.r.t.\ continuous
variables is newer and less known: along with the family
described here, other methods include moderated factor
models \cite{bauhus09,moldol10,pur02} and factor mixture models
\cite{dolmaa98,lubmut05}.  These methods require estimation of a model
of greater complexity, while the tests described in this paper work solely
on the output of a traditional factor model \cite<see>[for
further comparison of these methods]{MerZei13}.

The family of tests described here have recently been applied
to the study of measurement invariance \cite{MerZei13,MerFanZei}, though their
practical application has been limited to a small set of simulations and
data examples.  In this paper, we provide a detailed illustration of
the tests' use and performance under
scenarios likely to be encountered in practice.  While the previous
papers have described and studied the tests under ideal conditions, we
focus here on two topics of interest to the applied researcher:
software considerations for carrying out the tests, and test
performance under model misspecification.
%In order to fix the psychometric scale, we need to specify the violating parameter.  
%Moreover, in practice model misspecification is an inevitable issue to a certain extent 
%and may interfere with parameter invariance specificity. A family of tests derived from 
%stochastic process has been recently proposed to identify specific parameters impacted 
%by measurement invariance violation. However, these tests have only been used to a limited 
%type of parameter violation. It is this paper's intent to provide a detailed examination 
%of the tests' performance under practical research scenarios. 
In the following sections, we first briefly review the  theoretical framework of
the proposed tests and provide a short tutorial illustrating the use of the
tests in \proglang{R} \cite{R11}. Next, we study the tests' performance in simulations that mimic
practical research scenarios.  Finally, we provide some further discussion on
the tests' use in practice.  We acknowledge 
problems associated with $p$-values (e.g., corrections for multiple
tests, researcher degrees of freedom, interpretations, etc) but
ignore them throughout the paper for expository purposes.

@@

To verbally describe Equation~\eqref{eq:score}, each
individual has $k$ scores describing the extent to which the fitted
model describes that particular individual.  We can roughly interpret
scores near zero as providing a ``good'' description of an individual,
with scores far from zero providing a ``bad'' description of an
individual.  This is only a rough interpretation as, even when measurement
invariance holds, some individuals' scores will be further from zero
than others.  However, under measurement noninvariance, the scores
will differ for different subgroups of individuals (say, scores in
subgroup A tend to be negative and scores in subgroup B tend to be
positive).  Each of the $k$ scores represents one model parameter,
which, as further described below, allows us to test subsets of model
parameters for invariance.  While scores can be obtained
under the multivariate normal likelihood (discrepancy) function and
alternatives such as generalized least squares, most SEM software
fails to supply the scores to the user.

To use the scores for testing, we order individuals according to
an auxiliary variable $V$ (the variable against which we are testing 
measurement invariance) and look for ``trends'' in the
scores.  For example, imagine that we are testing
for measurement 
invariance w.r.t.\ age.  If there exists measurement non-invariance
w.r.t. age, then some parameter estimates may be too large for 
young individuals and too small for old individuals (say).  This
result would be reflected in the scores, where young individuals'
scores may be greater than zero and old individuals' scores 
less than zero (though the sign of the scores will depend on whether a
function is being minimized or maximized).  Conversely, if measurement
invariance holds, then all 
individuals' scores will fluctuate randomly around zero.

@@

In addition to test statistics, ``instability plots'' can be generated
by setting 
\code{plot = TRUE} in the \code{sctest()} calls
above. Figure~\ref{fig:ordres} displays the resulting plots, which represent
the ordinal statistics' fluctuations across levels of age group.
The x-axis
reflects age group and the y-axis reflects test statistic values (larger
values reflect more instability), with the dashed horizontal lines
reflecting critical values.  The
hypothesis of measurement invariance is rejected if the sequence of
test statistics crosses the critical value.  While the measurement invariance tests are
non-significant, the plots imply some instability in the older age groups (15 and~16).

@@

\section{Simulation 1}
In Simulation 1, we examined the extent to which the proposed tests
can ``localize'' a measurement invariance violation.
If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameter estimates, including factor covariances, intercepts or 
the unique variance associated with the manifest variable in question.  
Thus, the goal of the Simulation 1 is to examine the extent to which 
the proposed tests attribute the measurement invariance violation 
to the parameters that are truly in violation.

@@

To examine these issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of four places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the intercept ($\mu_{11}$),
 the unique variance  ($\psi_{11}$), or the factor covariance
 ($\phi_{12}$).  Note that the 
 latter violation is not necessarily a measurement invariance
 \cite<e.g.,>{mer93}, but it is still a parameter instability that can occur in
 this type of model.
 We then tested for measurement invariance (parameter instability) in
 seven subsets of parameters: each of the four
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
all six unique variances and all six intercepts. % $\epsilon_{11}--\epsilon_{66}$.

@@

Full simulation results are presented in Figures~\ref{fig:sim11res}
to~\ref{fig:sim14res}.
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude in the factor loading $\lambda_{11}$,
with the parameters being tested changing across rows,
the number of levels $m$ of the ordinal variable $V$ across columns,
and lines reflecting different test statistics.
Figure~\ref{fig:sim12res}, Figure~\ref{fig:sim13res}, and 
Figure~\ref{fig:sim14res} display 
similar power curves when the factor covariance 
$\phi_{12}$, error variance $\epsilon_{11}$, and intercept
$\mu_{11}$ violate measurement
invariance, respectively. In these figures, we generally show tests
associated with parameters that exhibited nonzero power curves.  For
example, in Figure~\ref{fig:sim11res}, the middle row shows that power
for tests of $\psi_{11}$ stays near zero for all values of $m$ and $d$.
Similar rows have been omitted from this figure and other figures.

@@

From these figures, one generally observes that the tests isolate 
the parameter violating measurement invariance.  Additionally, the tests 
have somewhat higher power to detect measurement invariance violations 
in the factor loading, factor covariance, and intercept parameters, 
as opposed to the error variance parameter.  
Finally, simultaneous tests of all factor loadings, all intercepts, or 
all error parameters result in decreased power, as compared to the situation
where one tests only the violating parameter.  This occurs because, in
testing a subset of parameters (only one of which violates measurement
invariance), we are dampening the signal of a measurement
invariance violation. This ``dampening'' effect is more apparent for
the $\max \mathit{LM}_o$ statistic, because it involves a sum across
all tested parameters (see Equation~\eqref{eq:maxlmo}).
Conversely, $\mathit{WDM}_o$ takes the maximum over parameters
(Equation~\eqref{eq:wdm}), so that invariant parameters have no
impact on this statistic.

@@

\subsection{Method}
A measurement invariance violation could occur in
each of the four parameters from Simulation 1 (factor loading, factor
covariance, unique variance, and intercept), and a violation could also occur in
the extra, unmodeled loading. In each condition, a single parameter
exhibited the violation. 
Sample size and magnitude of measurement invariance violation were manipulated 
in the same way as they were in Simulation 1.  The tested parameters
were also the same as Simulation 1.

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error is also observed when testing all loadings and all unique
variances (see the Appendix).  Tests
associated with the factor 
covariance and intercept did not demonstrate this error, however.  In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

When the parameter violating measurement invariance was modeled,
results were generally the same as Simulation 1.  
When the modeled factor loading, $\lambda_{11}$, violated measurement
invariance, the statistics were generally able to pick up the violation despite
the misspecification. Similar results were observed
when the unique variance, intercept and factor covariance parameters violated measurement
invariance; these results are all shown in the Appendix.
In particular, power of the ordered statistics was higher than power
of the unordered statistic in 
each panel.

In summary, the proposed test statistics appear robust to unmodeled
loading parameters, so long 
as the unmodeled loading does not violate measurement invariance.  If
the unmodeled loading  
does violate measurement invariance, the tests can still detect
measurement invariance violations.  The violations are assigned to 
modeled parameters that do not violate measurement invariance, however.
The impacted parameters include the error 
variance and other loadings associated with the manifest variable that
has an unmodeled loading.
Thus, as for other tests of measurement invariance, it is important to
study the extent to 
which the hypothesized model includes all parameters of importance
(i.e., the extent to which the model is well specified).

One could begin to study model misspecification by fitting models with
different discrepancy functions (say, a multivariate normal function and a
generalized least squares function).  If parameter estimates differ
greatly across the functions, then this implies model
misspecification.  Additionally, if one has a large sample size, one
could split the data into subgroups and examine consistency of results
across subgroups.  These issues are important for all the tests
discussed here (score-based or otherwise).

@@

In the remainder of the paper, we first compare the use
these tests to the use of traditional tests in practice.  We then 
discuss test extension to other fit functions and to other specialized
models.

@@

Many of the applications in this volume, along with many measurement
invariance applications in
general, focus on testing across unordered categories
such as nations or gender.  As discussed earlier in this paper, the score-based
tests for unordered categories are equivalent to the usual
likelihood ratio test.  Given a measurement invariance violation across these
unordered categories, however, researchers typically wish to know why the
violation occurred.  At this point, researchers may examine education level,
socioeconomic status, income levels, and so on across the unordered categories. 
These variables are often ordinal or continuous in nature, so that the family of
tests described in this paper are applicable.  This is a first step towards
describing why measurement invariance violations occur, as opposed to simply
detecting measurement invariance violations. 
%% TODO!!
%\readme{In the abstracts for the
%special issue (which the special editors sent us), one paper was proposed along
%these lines.  I will get a draft of that paper and then we can cite it here.}
The tests described here are convenient for this purpose, as they do
not require a new model to 
be estimated for each ordinal variable.  Instead, each ordinal variable defines
an ordering of observations, which in turn yields a test statistic that is
specific to that ordinal variable.

@@

In addition to alternative fit functions, the tests can be extended to other
models estimated via ML.  Of primary interest to the topic of measurement
invariance, the tests can be extended to item response models to examine
differential item functioning.  In particular, \citeA{strkop13} studied
application of these tests to the Rasch model, using them as the basis of a
recursive partitioning procedure that segments subgroups of individuals who
exhibit DIF.  Further study and extension of these tests for IRT are warranted.

@@

This Appendix contains additional results from Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figures~\ref{fig:sim22res} to~\ref{fig:sim26res} display
results when the unmodeled loading, the loading $\lambda_{11}$, the
covariance $\phi_{12}$, the error term $\psi_{11}$, and the intercept $\mu_{11}$
violate invariance, respectively.  Results are only shown for simulation
conditions exhibiting power curves that increased from zero.  These
results were generally the same as the Simulation 1 results.
